The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-11 paper/mri paper.tex
more solvability criteria

must be satisfied in order for Equation \ref{ordere2} to have a solution.

>>>>

must be satisfied in order for Equation \ref{ordere2} to have a solution. In the above,

\beq
\mathbf{V}^\dagger = \mathbb{V}^\dagger e^{iQz} + c.c.
\eeq

The elimination of this inner product must also be enforced the terms in Equation \ref{ordere3} that are resonant with $e^{i k_c z}$, yielding

\beq
\label{ampeq1}
a \partial_T \alpha \, + \, c \alpha \left|\alpha^2\right| \, + \, \widetilde{c} \alpha \partial_Z \beta \, = \, - b \partial_Z \alpha \, + \, h \partial_Z^2 \alpha \, + \, g i Q^3 \alpha
\eeq

\begin{multline}
a \equiv \left< \mathbb{V}^\dagger \cdot \mathcal{D}\mathbb{V}^*_{11}\right> \\
c \equiv \left< \mathbb{V}^\dagger \cdot \mathbf{N}^*_{31}\right> \\
\widetilde{c} \equiv \left< \mathbb{V}^\dagger \cdot \widetilde{\mathbf{N}}^*_{31}\right> \\
b \equiv \left< \mathbb{V}^\dagger \cdot \left(\mathcal{X}\mathbb{V}_{11}\right)^* \right> \\
h \equiv \left< \mathbb{V}^\dagger \cdot \left(\widetilde{\mathcal{L}}_2\mathbb{V}_{11} \, - \, \widetilde{\mathcal{L}}_1\mathbb{V}_{21} \right)^* \right> \\
g \equiv \left< \mathbb{V}^\dagger \cdot \mathcal{L}_{3} \mathbb{V}_{11} \right> \\
\end{multline}

Equation \ref{ampeq1} is an amplitude equation -- a function of the slow variables $Z$ and $T$. We solve this initial value problem using Dedalus to obtain the asymptotic behavior of $\alpha$. This is the saturation amplitude.
